---
title: "Prediction On Resale Flat Price"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

References:

<br>1. https://statsandr.com/blog/descriptive-statistics-in-r/
<br>2. https://towardsdatascience.com/data-cleaning-with-r-and-the-tidyverse-detecting-missing-values-ea23c519bc62
<br>3. https://rstudio-pubs-static.s3.amazonaws.com/3364_d1a578f521174152b46b19d0c83cbe7e.html
<br>4. https://medium.com/data-science-in-your-pocket/various-data-distributions-in-statistics-362dc92558db
<br>5. https://stackoverflow.com/questions/5570293/add-column-which-contains-binned-values-of-an-integer-column

***
## Import Libraries

```{r}
library(tidyr)
library(tidyverse)
library(summarytools)
library(car)
library(dlookr)
library(ggplot2)
library(plyr)
```

***
# Data Cleaning

## Read CSV

```{r}
data_2015_2016 <- read.csv("../data/resale-flat-prices-based-on-registration-date-from-jan-2015-to-dec-2016.csv", header = TRUE, sep = ",")
data_2017 <- read.csv("../data/resale-flat-prices-based-on-registration-date-from-jan-2017-onwards.csv", header = TRUE, sep = ",")

data_info <- read.csv("../data/hdb-property-information.csv", header = TRUE, sep = ",")
```

## Data Columns Exploration

```{r}
print("data_2015_2016:")
str(data_2015_2016)
print("data_2017:")
str(data_2017)
print("data_info:")
str(data_info)

```
## Data Preprocessing Before Data Integration

Transform the remaining lease to month for data_2015_2016.
```{r}
data_2015_2016$remaining_lease <- data_2015_2016$remaining_lease * 12
str(data_2015_2016$remaining_lease)
```
Transform the remaining lease to month for data_2017.
```{r}
convert_remaining_lease <- function(remaining_lease) {
  lease <- trimws(remaining_lease)
  year <- substr(lease, 0, 2)
  
  
  result <- ifelse(grepl("month", lease), as.integer(year) * 12 + as.integer(substr(lease, 9, 11)) , as.integer(year) * 12)
  return(result)
}

data_2017$remaining_lease <- convert_remaining_lease(data_2017$remaining_lease)
str(data_2017$remaining_lease)
```

Drop columns from data_info that are not contributing for resale price prediction.
```{r}
data_info <- data_info %>% select(c("bldg_contract_town", "street", "blk_no", "max_floor_lvl", "commercial", "market_hawker", "miscellaneous", "multistorey_carpark", "precinct_pavilion"))
str(data_info)
```
Convert Y/N to binary.
```{r}

data_info$commercial <- ifelse(data_info$commercial == "Y", 1, 0)
data_info$market_hawker <- ifelse(data_info$market_hawker == "Y", 1, 0)
data_info$miscellaneous <- ifelse(data_info$miscellaneous == "Y", 1, 0)
data_info$multistorey_carpark <- ifelse(data_info$multistorey_carpark == "Y", 1, 0)
data_info$precinct_pavilion <- ifelse(data_info$precinct_pavilion == "Y", 1, 0)

str(data_info)

```
Convert town in short form to full text
```{r}

town_short <- c("AMK","BB","BD","BH","BM","BP","BT","CCK","CL","CT","GL","HG","JE","JW","KWN","MP","PG","PRC","QT","SB","SGN","SK","TAP","TG","TP","WL","YS")
town_full <- c( "ANG MO KIO","BUKIT BATOK","BEDOK","BISHAN","BUKIT MERAH","BUKIT PANJANG","BUKIT TIMAH","CHOA CHU KANG","CLEMENTI","CENTRAL AREA","GEYLANG","HOUGANG","JURONG EAST","JURONG WEST","KALLANG/WHAMPOA","MARINE PARADE","PUNGGOL","PASIR RIS","QUEENSTOWN","SEMBAWANG","SERANGOON","SENGKANG","TAMPINES","TENGAH","TOA PAYOH","WOODLANDS","YISHUN")

data_info$bldg_contract_town <- mapvalues(data_info$bldg_contract_town, from=town_short, to=town_full)
str(data_info$bldg_contract_town)

unique(sort(data_info$bldg_contract_town))
unique(sort(data_2015_2016$town))
unique(sort(data_2017$town))

```

## Data Integration

Merge both resale price datasets.
```{r}
data <- rbind(data_2015_2016, data_2017)
str(data)
```

Join the resale price dataset and HDB property information dataset.
```{r}

names(data_info)[names(data_info) == "bldg_contract_town"] <- "town"
names(data_info)[names(data_info) == "street"] <- "street_name"
names(data_info)[names(data_info) == "blk_no"] <- "block"

data = merge(x = data, y = data_info, by = c("town","street_name","block"))
str(data)
```
The merged dataset contains total 152,455 observations (flat resales transaction) and 17 variables.

## Data Exploration To Detect Incorrect Data, Handling Incorrect Data, and Transforming Data

```{r}
summary(data)
head(data)
tail(data)
```
***

### 1. month
```{r}
head(data$month)
tail(data$month)
```
  * split into two columns - year and month
  * convert year and month from char to factor
```{r}
data <- data %>% separate(month, c("year","month"), "-")
head(data)
str(data$year)
str(data$month)

unique(sort(data$year))
unique(sort(data$month))

data %>% summarise(na_year = sum(is.na(year)),
                   na_month = sum(is.na(month)))

data$int_year <- as.integer(data$year)

data$year <- as.factor(data$year)
data$month <- as.factor(data$month)
str(data$year)
str(data$month)

sort(summary(data$year))
sort(summary(data$month))
```
  * there's no missing value
  * exploration of year by plotting
```{r}
barplot(table(data$year), ylim=c(0,30000), las = 2)

p <- ggplot(data, aes(x = fct_infreq(year), fill = fct_infreq(year))) +
  geom_bar(width = 1, colour = "black", show.legend = FALSE) +
  xlab("year")

p + coord_flip() + scale_y_continuous(limit = c(0, 30000))
``` 

  * exploration of month by plotting
```{r}
barplot(table(data$month), ylim=c(0,20000), las = 2)

p <- ggplot(data, aes(x = fct_infreq(month), fill = fct_infreq(month))) +
  geom_bar(width = 1, colour = "black", show.legend = FALSE) +
  xlab("month")

p + coord_flip() + scale_y_continuous(limit = c(0, 20000))
``` 

  * uniform distribution type
  * the transaction records in every month are about the same, ranges from 9,000 to 15,000
  * July has the highest transaction records
  * February has the lowest transaction records
  
### 2. town
```{r}
head(data$town)
tail(data$town)
str(data$town)
```  
  * explore the number of distinct values of town
  * convert to factor
```{r}
data %>% distinct(town)

data %>% summarise(na = sum(is.na(town)))

data$town <- as.factor(data$town)

str(data$town)
sort(summary(data$town))
```
  * there's no missing value
  * exploration by plotting
```{r}
p <- ggplot(data, aes(x = fct_infreq(town), fill = fct_infreq(town))) +
  geom_bar(width = 1, colour = "black", show.legend = FALSE) +
  xlab("town")

p + coord_flip() + scale_y_continuous(limit = c(0, 15000))

# Zoom in to town with frequency < 10,000
data_filter <- data %>% 
  group_by(town) %>%
  filter(n() < 8000)

p <- ggplot(data_filter, aes(x = fct_infreq(town), fill = fct_infreq(town))) +
  geom_bar(width = 1, colour = "black", show.legend = FALSE) +
  xlab("town")

p + coord_flip() + scale_y_continuous(limit = c(0, 8000))

``` 

  * SENGKANG  has the highest transaction records, more than 10,000 rows
  * BUKIT TIMAH has the lowest transaction records, less than 1,000 rows
  
  * classify towns into region (refer to https://www.mappr.co/counties/regions-of-singapore/)
  * classify BUKIT TIMAH as central region (refer to https://en.wikipedia.org/wiki/Bukit_Timah)
```{r}
data$region <- ifelse (data$town %in% c("BUKIT MERAH","BUKIT TIMAH","GEYLANG","TOA PAYOH",
                                        "BISHAN","KALLANG/WHAMPOA","MARINE PARADE", "CENTRAL AREA", "QUEENSTOWN"), "Central",
                       ifelse (data$town %in% c("TAMPINES","BEDOK","PASIR RIS"), "East",
                               ifelse (data$town %in% c("LIM CHU KANG","SEMBAWANG","WOODLANDS","YISHUN"), "North",
                                       ifelse (data$town %in% c("ANG MO KIO","HOUGANG","PUNGGOL","SENGKANG",
                                                                "SERANGOON"), "North-East",
                                               ifelse (data$town %in% c("BUKIT BATOK","BUKIT PANJANG",
                                                                        "CHOA CHU KANG","CLEMENTI",
                                                                        "JURONG EAST","JURONG WEST"), "West",
                                                       as.character(data$town))))))
                    
head(data)
head(data$region)
tail(data$region)
str(data$region)

data$region <- as.factor(data$region)

str(data$region)
sort(summary(data$region))

```
  * exploration by plotting
```{r}
p <- ggplot(data, aes(x = fct_infreq(region), fill = fct_infreq(region))) +
  geom_bar(width = 1, colour = "black", show.legend = FALSE) +
  xlab("region")

p + coord_flip() + scale_y_continuous(limit = c(0, 45000))

``` 

  * North-East has the highest transaction records, nearly 40,000 rows
  * East has the lowest transaction records, less than 25,000 rows

### 3. flat_type

```{r}
head(data$flat_type)
tail(data$flat_type)
str(data$flat_type)
```  
  * explore the number of distinct values of flat type
```{r}
data %>% distinct(flat_type)

data %>% summarise(na = sum(is.na(flat_type)))
```
  * there's no missing value
  * convert to factor
```{r}
data$flat_type <- as.factor(data$flat_type)

str(data$flat_type)
sort(summary(data$flat_type))
```

  * exploration by plotting
```{r}
p <- ggplot(data, aes(x = fct_infreq(flat_type), fill = fct_infreq(flat_type))) +
  geom_bar(width = 1, colour = "black", show.legend = FALSE) +
  xlab("flat_type")

p + coord_flip() + scale_y_continuous(limit = c(0, 70000))

# Zoom in
data_filter <- data %>% 
  group_by(flat_type) %>%
  filter(n() < 100)

p <- ggplot(data_filter, aes(x = fct_infreq(flat_type), fill = fct_infreq(flat_type))) +
  geom_bar(width = 1, colour = "black", show.legend = FALSE) +
  xlab("flat_type")

p + coord_flip() + scale_y_continuous(limit = c(0, 100))
``` 

  * 4 ROOM type HDB has the highest transaction records, more than 60,000 rows
  * 1 ROOM type HDB has the lowest transaction records, less than 100 rows
  * both MULTI-GENERATION and 1 ROOM type HDB have less than 100 transaction records, it is logical as not much HDB in these two types

  * reference: https://www.hdb.gov.sg/residential/buying-a-flat/resale/getting-started/types-of-flats
  * MULTI-GENERATION:
  * Eligible multi-generation families living under one roof in a 3Gen flat can delight in closer family ties. With 2 bedrooms with attached bathrooms, and 2 other bedrooms, it easily supports the needs of larger households.

### 4. block

```{r}
head(data$block)
tail(data$block)
str(data$block)
```  
  * explore the number of distinct values of block
  * convert to factor
```{r}
data %>% 
  distinct(block) %>%
  head()

data %>% 
  distinct(block) %>%
  tail()

data %>% summarise(na = sum(is.na(block)))

data$block <- as.factor(data$block)

str(data$block)
sort(summary(data$block))
```
  * there's no missing value
  * remove the alphabet in block number to reduce the number of unique value

```{r}
data$block <- gsub("[^0-9.-]", "", data$block)
data$block <- as.factor(data$block)

data %>% 
  distinct(block) %>%
  head()

data %>% 
  distinct(block) %>%
  tail()

str(data$block)
sort(summary(data$block))
```

  * exploration by plotting
  * select blocks of top 10 highest transaction records and top 10 lowest transaction records
```{r}
groupby_block <- data  %>% 
     group_by(block) %>%
     dplyr::summarise(n = n()) %>%
     arrange(n, decreasing = TRUE)

top10 <- head(groupby_block,10)
btm10 <- tail(groupby_block,10)

# TOP 10 block with highest transactions
data_filter <- data %>% 
  filter(block %in% top10$block)

p <- ggplot(data_filter, aes(x = fct_infreq(block), fill = fct_infreq(block))) +
  geom_bar(width = 1, colour = "black", show.legend = FALSE) +
  xlab("block")

p + coord_flip() + scale_y_continuous(limit = c(0, 1000))

# BOTTOM 10 block with lowest transactions
data_filter <- data %>% 
  filter(block %in% btm10$block)

p <- ggplot(data_filter, aes(x = fct_infreq(block), fill = fct_infreq(block))) +
  geom_bar(width = 1, colour = "black", show.legend = FALSE) +
  xlab("block")

p + coord_flip() + scale_y_continuous(limit = c(0, 10))

``` 


### 5. street_name
```{r}
head(data$street_name)
tail(data$street_name)
str(data$street_name)
```  
  * explore the number of distinct values of street_name
  * convert to factor
```{r}
data %>% 
  distinct(street_name) %>%
  head()

data %>%
  distinct(street_name) %>%
  tail()

data %>% summarise(na = sum(is.na(street_name)))

data$street_name <- as.factor(data$street_name)

str(data$street_name)
sort(summary(data$street_name))
```
  * there's no missing value
  * exploration by plotting
  * select street name of top 10 highest transaction records and top 10 lowest transaction records
```{r}
groupby_street <- data  %>% 
     group_by(street_name) %>%
     dplyr::summarise(n = n()) %>%
     arrange(n, decreasing = TRUE)

top10 <- head(groupby_street,10)
btm10 <- tail(groupby_street,10)

# TOP 10 street_name with highest transactions
data_filter <- data %>% 
  filter(street_name %in% top10$street_name)

p <- ggplot(data_filter, aes(x = fct_infreq(street_name), fill = fct_infreq(street_name))) +
  geom_bar(width = 1, colour = "black", show.legend = FALSE) +
  xlab("street_name")

p + coord_flip() + scale_y_continuous(limit = c(0, 3000))

# BOTTOM 10 street_name with lowest transactions
data_filter <- data %>% 
  filter(street_name %in% btm10$street_name)

p <- ggplot(data_filter, aes(x = fct_infreq(street_name), fill = fct_infreq(street_name))) +
  geom_bar(width = 1, colour = "black", show.legend = FALSE) +
  xlab("street_name")

p + coord_flip() + scale_y_continuous(limit = c(0, 20))

``` 

### 6. storey_range
```{r}
head(data$storey_range)
tail(data$storey_range)
str(data$storey_range)
```  
  * explore the number of distinct values of storey_range
```{r}
unique(sort(data$storey_range))
data %>% summarise(na = sum(is.na(storey_range)))
```
  * there's no missing value
  * convert storey_range to factor
```{r}

data$storey_range <- as.factor(data$storey_range)
sort(summary(data$storey_range))
```
  * exploration by plotting
```{r}
barplot(table(data$storey_range), ylim=c(0,50000), las = 2)

p <- ggplot(data, aes(x = fct_infreq(storey_range), fill = fct_infreq(storey_range))) +
  geom_bar(width = 1, colour = "black", show.legend = FALSE) +
  xlab("storey_range")

p + coord_flip() + scale_y_continuous(limit = c(0, 50000))

# Zoom in
data_filter <- data %>% 
  group_by(storey_range) %>%
  filter(n() < 3000)

p <- ggplot(data_filter, aes(x = fct_infreq(storey_range), fill = fct_infreq(storey_range))) +
  geom_bar(width = 1, colour = "black", show.legend = FALSE) +
  xlab("storey_range")

p + coord_flip() + scale_y_continuous(limit = c(0, 3000))
```

  * Storey range of 04 TO 06 has the highest transaction records, more than 35,000 rows
  * Storey range of 49 TO 51 has the lowest transaction records, less than 500 rows
  * Storey range from 01 TO 12 has higher transaction records compared to other floor level

  
### 7. floor_area_sqm

```{r}
head(data$floor_area_sqm)
tail(data$floor_area_sqm)
str(data$floor_area_sqm)

data %>% summarise(na = sum(is.nan(floor_area_sqm)))
summary(data$floor_area_sqm)
```
  * there's no missing value
  * exploration by plotting
```{r}
barplot(table(data$floor_area_sqm), ylim=c(0,10000), las = 2)

data_plot <- data

data_plot$floor_area_sqm <- as.factor(data_plot$floor_area_sqm)
p <- ggplot(data_plot, aes(x = fct_infreq(floor_area_sqm), fill = fct_infreq(floor_area_sqm))) +
  geom_bar(width = 1, colour = "black", show.legend = FALSE) +
  xlab("floor_area_sqm")

p + coord_flip() + scale_y_continuous(limit = c(0, 10000))

# Zoom in
data_filter <- data_plot %>% 
  group_by(floor_area_sqm) %>%
  filter(n() < 20)

p <- ggplot(data_filter, aes(x = fct_infreq(floor_area_sqm), fill = fct_infreq(floor_area_sqm))) +
  geom_bar(width = 1, colour = "black", show.legend = FALSE) +
  xlab("floor_area_sqm")

p + coord_flip() + scale_y_continuous(limit = c(0, 20))
```
  
  * binning
```{r}
summary(data$floor_area_sqm)
max(data$floor_area_sqm) -  min(data$floor_area_sqm)

lower_boundary <- c(seq(30, 270, by=20))
upper_boundary <- c(seq(50, 300, by=20))
lower_boundary
upper_boundary


bin_label <- c(paste(paste(lower_boundary, "-"),upper_boundary))
bin_label

data$floor_area_sqm_bins <- cut(data$floor_area_sqm, breaks=c(seq(30, 300, by=20)), labels=bin_label)

data %>% select(floor_area_sqm, floor_area_sqm_bins) %>% head()

str(data$floor_area_sqm_bins)
summary(data$floor_area_sqm_bins)

data %>% filter(is.na(floor_area_sqm_bins)) %>% select(floor_area_sqm, floor_area_sqm_bins) %>% head()
```

```{r}
barplot(table(data$floor_area_sqm_bins), ylim=c(0,60000), las = 2)

p <- ggplot(data, aes(x = fct_infreq(floor_area_sqm_bins), fill = fct_infreq(floor_area_sqm_bins))) +
  geom_bar(width = 1, colour = "black", show.legend = FALSE) +
  xlab("floor_area_sqm")

p + coord_flip() + scale_y_continuous(limit = c(0, 60000))

# Zoom in to
data_filter <- data %>% 
  group_by(floor_area_sqm_bins) %>%
  filter(n() < 50)

p <- ggplot(data_filter, aes(x = fct_infreq(floor_area_sqm_bins), fill = fct_infreq(floor_area_sqm_bins))) +
  geom_bar(width = 1, colour = "black", show.legend = FALSE) +
  xlab("floor_area_sqm")

p + coord_flip() + scale_y_continuous(limit = c(0, 50))
```

  * Floor area (sqm) from 90-110 has the highest transaction records, more than 50,000 rows
  * Floor area (sqm) from 250-290 has the lowest transaction records, less than 5 rows
  * Most of the HDB has floor area ranges from 50-150 sqm
  
  * Create new column - price per sqm
```{r}
data$price_per_sqm <- round(data$resale_price / data$floor_area_sqm, 2)
head(data)
tail(data)
str(data$price_per_sqm)

```

  * exploration by plotting
```{r}
barplot(table(data$price_per_sqm), ylim=c(0,1500), las = 2)

```  
  
  
### 8. flat_model
```{r}
head(data$flat_model)
tail(data$flat_model)
str(data$flat_model)
```  
  * explore the number of distinct values of flat_model
```{r}
unique(sort(data$flat_model))
data %>% summarise(na = sum(is.na(flat_model)))
```
  * there's no missing value
  * convert to factor
```{r}
data$flat_model <- as.factor(data$flat_model)

str(data$flat_model)
sort(summary(data$flat_model))
```
  * exploration by plotting
```{r}
p <- ggplot(data, aes(x = fct_infreq(flat_model), fill = fct_infreq(flat_model))) +
  geom_bar(width = 1, colour = "black", show.legend = FALSE) +
  xlab("flat_model")

p + coord_flip() + scale_y_continuous(limit = c(0, 60000))

# Zoom in
data_filter <- data %>%
  group_by(flat_model) %>%
  filter(n() < 3000)

p <- ggplot(data_filter, aes(x = fct_infreq(flat_model), fill = fct_infreq(flat_model))) +
  geom_bar(width = 1, colour = "black", show.legend = FALSE) +
  xlab("flat_model")

p + coord_flip() + scale_y_continuous(limit = c(0, 3000))
```

### 9. lease_commence_date

```{r}
head(data$lease_commence_date)
tail(data$lease_commence_date)
str(data$lease_commence_date)

unique(sort(data$lease_commence_date))
data %>% summarise(na = sum(is.na(lease_commence_date)))
summary(data$lease_commence_date)

# check whether remaining lease is calculated correctly
data %>%
  filter(!is.na(remaining_lease) && remaining_lease != (99 - (data$int_year - data$lease_commence_date))) %>% 
  select(remaining_lease)
```
  * there's no missing value

### 10. resale_price

```{r}
head(data$resale_price)
tail(data$resale_price)
str(data$resale_price)

data %>% summarise(na = sum(is.na(resale_price)))
summary(data$resale_price)

```
  * there's no missing value
  * exploration by plotting
```{r}
barplot(table(data$resale_price), ylim=c(0,3000), las = 2)

```
  
  * binning
```{r}
summary(data$resale_price)
max(data$resale_price) -  min(data$resale_price)

lower_boundary <- c(seq(79000, 1360000, by=61000))
upper_boundary <- c(seq(140000, 1421000, by=61000))
lower_boundary
upper_boundary

bin_label <- c(paste(paste(lower_boundary, "-"),upper_boundary))
bin_label

data$resale_price_bins <- cut(data$resale_price, breaks=c(seq(79000, 1421000, by=61000)), labels=bin_label)
 
data %>% select(resale_price, resale_price_bins) %>% head()
 
str(data$resale_price_bins)
summary(data$resale_price_bins)

data %>% filter(is.na(resale_price_bins)) %>% select(resale_price, resale_price_bins) %>% head()

```

  * exploration by plotting
```{r}
barplot(table(data$resale_price_bins), ylim=c(0,35000), las = 2)

p <- ggplot(data, aes(x = fct_infreq(resale_price_bins), fill = fct_infreq(resale_price_bins))) +
  geom_bar(width = 1, colour = "black", show.legend = FALSE) +
  xlab("resale_price")

p + coord_flip() + scale_y_continuous(limit = c(0, 35000))

# Zoom in
data_filter <- data %>%
  group_by(resale_price_bins) %>%
  filter(n() < 500)

p <- ggplot(data_filter, aes(x = fct_infreq(resale_price_bins), fill = fct_infreq(resale_price_bins))) +
  geom_bar(width = 1, colour = "black", show.legend = FALSE) +
  xlab("resale_price")

p + coord_flip() + scale_y_continuous(limit = c(0, 500))
```

  * Resale price ranges from 384000-445000 has the highest transaction records, more than 30,000 rows
  * Resale price ranges from 1299000-1360000 has the lowest transaction records, less than 50 rows
  * Most of the HDB resale with price ranges from 262000-567000

```{r}
boxplot(data$resale_price ~ data$year)
boxplot(data$resale_price ~ data$region)
boxplot(data$resale_price ~ data$floor_area_sqm_bins)
```
  
  * correlation between variables
  
```{r}
ggplot(data) +
  aes(x = floor_area_sqm, y = resale_price, colour = flat_type) +
  geom_point() +
  scale_color_hue()

ggplot(data) +
  aes(x = max_floor_lvl, y = resale_price, colour = flat_type) +
  geom_point() +
  scale_color_hue()

ggplot(data) +
  aes(x = remaining_lease, y = resale_price, colour = flat_type) +
  geom_point() +
  scale_color_hue()

ggplot(data) +
  aes(x = floor_area_sqm, y = resale_price, colour = region) +
  geom_point() +
  scale_color_hue()

ggplot(data) +
  aes(x = max_floor_lvl, y = resale_price, colour = region) +
  geom_point() +
  scale_color_hue()

ggplot(data) +
  aes(x = remaining_lease, y = resale_price, colour = region) +
  geom_point() +
  scale_color_hue()
```

### 11. remaining_lease

```{r}
head(data$remaining_lease)
tail(data$remaining_lease)
str(data$remaining_lease)

data %>% summarise(na = sum(is.na(remaining_lease)))
summary(data$remaining_lease)

```

  * exploration by plotting
```{r}
data_plot <- data
data_plot$remaining_lease <- as.integer(data$remaining_lease / 12)

barplot(table(data_plot$remaining_lease), ylim=c(0,10000), las = 2)

data_plot$remaining_lease <- as.factor(data_plot$remaining_lease)
p <- ggplot(data_plot, aes(x = fct_infreq(remaining_lease), fill = fct_infreq(remaining_lease))) +
  geom_bar(width = 1, colour = "black", show.legend = FALSE) +
  xlab("remaining_lease")

p + coord_flip() + scale_y_continuous(limit = c(0, 10000))

# Zoom in 
data_filter <- data_plot %>% 
  group_by(remaining_lease) %>%
  filter(n() < 100)

p <- ggplot(data_filter, aes(x = fct_infreq(remaining_lease), fill = fct_infreq(remaining_lease))) +
  geom_bar(width = 1, colour = "black", show.legend = FALSE) +
  xlab("remaining_lease")

p + coord_flip() + scale_y_continuous(limit = c(0, 100))
```
  
  * 94 remaining lease year has the highest transaction records, more than 8,000 rows
  * 97 remaining lease year has the lowest transaction records, less than 20 rows
  * remaining lease year > 96 has very low transaction records, should be due to the restriction to sell the HDB if purchased less than N years

### 12. max_floor_lvl

```{r}
head(data$max_floor_lvl)
tail(data$max_floor_lvl)
str(data$max_floor_lvl)

data %>% summarise(na = sum(is.na(max_floor_lvl)))
summary(data$max_floor_lvl)

```

  * there's no missing value
  * exploration by plotting
```{r}

barplot(table(data$max_floor_lvl), ylim=c(0,40000), las = 2)

data_plot <- data
data_plot$max_floor_lvl <- as.factor(data_plot$max_floor_lvl)
p <- ggplot(data_plot, aes(x = fct_infreq(max_floor_lvl), fill = fct_infreq(max_floor_lvl))) +
  geom_bar(width = 1, colour = "black", show.legend = FALSE) +
  xlab("max_floor_lvl")

p + coord_flip() + scale_y_continuous(limit = c(0, 40000))

# Zoom in 
data_filter <- data_plot %>% 
  group_by(max_floor_lvl) %>%
  filter(n() < 100)

p <- ggplot(data_filter, aes(x = fct_infreq(max_floor_lvl), fill = fct_infreq(max_floor_lvl))) +
  geom_bar(width = 1, colour = "black", show.legend = FALSE) +
  xlab("max_floor_lvl")

p + coord_flip() + scale_y_continuous(limit = c(0, 100))
```

  * 12 max floor level has the highest transaction records, more than 30,000 rows
  * 48 max floor level has the lowest transaction records, less than 20 rows
  * Most of the HDB are having 10-18 max floor levels

### 13. commercial

```{r}
head(data$commercial)
tail(data$commercial)
str(data$commercial)
unique(data$market_hawker)

data %>% summarise(na = sum(is.na(commercial)))

```

  * there's no missing value
  * exploration by plotting
```{r}
barplot(table(data$commercial), ylim=c(0,150000), las = 2)

ggplot(data = data, aes(x = factor(commercial), fill = factor(commercial))) +
geom_bar(aes(y = (..count..)/sum(..count..)),
         position = "dodge") + 
geom_text(aes(y = (..count..)/sum(..count..), 
              label = paste0(round(prop.table(..count..) * 100,2), '%')), 
          stat = 'count', 
          position = position_dodge(.9), 
          size = 3)+ 
labs(x = 'commercial', y = 'Percent', fill = 'commercial')

```
  * Most of the HDB are far away from commercial area


### 14. market_hawker

```{r}
head(data$market_hawker)
tail(data$market_hawker)
str(data$market_hawker)
unique(data$market_hawker)

data %>% summarise(na = sum(is.na(market_hawker)))

```
  * there's no missing value
  * exploration by plotting
```{r}
barplot(table(data$market_hawker), ylim=c(0,200000), las = 2)
barplot(table(data$market_hawker), ylim=c(0,100), las = 2)

ggplot(data = data, aes(x = factor(market_hawker), fill = factor(market_hawker))) +
geom_bar(aes(y = (..count..)/sum(..count..)),
         position = "dodge") + 
geom_text(aes(y = (..count..)/sum(..count..), 
              label = paste0(round(prop.table(..count..) * 100,2), '%')), 
          stat = 'count', 
          position = position_dodge(.9), 
          size = 3)+ 
labs(x = 'market_hawker', y = 'Percent', fill = 'market_hawker')

```

  * Most of the HDB are far away from market and hawker area

### 15. miscellaneous

```{r}
head(data$miscellaneous)
tail(data$miscellaneous)
str(data$miscellaneous)
unique(data$miscellaneous)

data %>% summarise(na = sum(is.na(miscellaneous)))

```

  * there's no missing value
  * exploration by plotting
```{r}
barplot(table(data$miscellaneous), ylim=c(0,120000), las = 2)

ggplot(data = data, aes(x = factor(miscellaneous), fill = factor(miscellaneous))) +
geom_bar(aes(y = (..count..)/sum(..count..)),
         position = "dodge") + 
geom_text(aes(y = (..count..)/sum(..count..), 
              label = paste0(round(prop.table(..count..) * 100,2), '%')), 
          stat = 'count', 
          position = position_dodge(.9), 
          size = 3)+ 
labs(x = 'miscellaneous', y = 'Percent', fill = 'miscellaneous')

```
  * Most of the HDB are far away from admin office, childcare centre, education centre, Residents' Committees centre, etc

### 16. multistorey_carpark

```{r}
head(data$multistorey_carpark)
tail(data$multistorey_carpark)
str(data$multistorey_carpark)
unique(data$multistorey_carpark)

data %>% summarise(na = sum(is.na(multistorey_carpark)))

```

  * there's no missing value
  * exploration by plotting
```{r}
barplot(table(data$multistorey_carpark), ylim=c(0,200000), las = 2)

ggplot(data = data, aes(x = factor(multistorey_carpark), fill = factor(multistorey_carpark))) +
geom_bar(aes(y = (..count..)/sum(..count..)),
         position = "dodge") + 
geom_text(aes(y = (..count..)/sum(..count..), 
              label = paste0(round(prop.table(..count..) * 100,2), '%')), 
          stat = 'count', 
          position = position_dodge(.9), 
          size = 3)+ 
labs(x = 'multistorey_carpark', y = 'Percent', fill = 'multistorey_carpark')

```

  * Most of the HDB do not have multistorey car park

### 17. precinct_pavilion

```{r}
head(data$precinct_pavilion)
tail(data$precinct_pavilion)
str(data$precinct_pavilion)
unique(data$precinct_pavilion)

data %>% summarise(na = sum(is.na(precinct_pavilion)))

```

  * there's no missing value
  * exploration by plotting
```{r}
barplot(table(data$precinct_pavilion), ylim=c(0,200000), las = 2)

ggplot(data = data, aes(x = factor(precinct_pavilion), fill = factor(precinct_pavilion))) +
geom_bar(aes(y = (..count..)/sum(..count..)),
         position = "dodge") + 
geom_text(aes(y = (..count..)/sum(..count..), 
              label = paste0(round(prop.table(..count..) * 100,2), '%')), 
          stat = 'count', 
          position = position_dodge(.9), 
          size = 3)+ 
labs(x = 'precinct_pavilion', y = 'Percent', fill = 'precinct_pavilion')

```

  * Most of the HDB do not have precinct pavilion

### Drop Columns
```{r}
str(data)
``` 
  * drop columns that are useless for prediction
```{r}
data <- data[,-which(names(data) %in% c("lease_commence_date","int_year","floor_area_sqm_bins","resale_price_bins"))]

```  

### Explore Cleaned Dataset

```{r}
summary(data)
str(data)

``` 

### Export Cleaned Dataset

```{r}
write.csv(data,"../data/data_clean.csv", row.names = FALSE)
```