---
title: "CorrelationAnalytics"
output: html_document
---
# Correlation Analytics for Property Price Factors

This R markdown file serves to provide correlation analytics using ***ANOVA** for the identification of important, relevant factors in predicting property prices

As some variable have unclear data, in order to decide on the significance of dropping/including it, we performed ANOVA analysis on the below factors to observe its correlation with the y value we predict, which is the resale price
- flat type
- flat model
- storey range
- street name

# Read dataset
```{r}
propertyprice = read.csv("C:\\Users\\Wei Wen\\Downloads\\resale-flat-prices\\resale-flat-prices-based-on-registration-date-from-jan-2017-onwards.csv")
```

# Simple EDA for dataset
```{r}
head(propertyprice)
```

# Correlation R value for floor area sqm with resale price
```{r}
plot(propertyprice$floor_area_sqm,propertyprice$resale_price)
cor(propertyprice$floor_area_sqm,propertyprice$resale_price)
cor.test(propertyprice$floor_area_sqm,propertyprice$resale_price)
```

# ANOVA Analysis
```{r}
street.aov <- aov(resale_price ~ street_name, data = propertyprice)
summary(street.aov)
flattype.aov <- aov(resale_price ~ flat_type, data = propertyprice)
summary(flattype.aov)
storey.aov <- aov(resale_price ~ storey_range, data = propertyprice)
summary(storey.aov)
flatmodel.aov <- aov(resale_price ~ flat_model, data = propertyprice)
summary(flatmodel.aov)
library(car)
ancova_model <- aov(resale_price ~ street_name + flat_type, data = propertyprice)
Anova(ancova_model, type="III")
```